### 2020-04-06 scache/jpdc/tex/intro.tex
some minor fixes
update

One of the major deficiency of the shuffle phase is lacking coordinated management among different system resources \cite{fu2018efficient}.

@@

{\color{black}
To optimize the data shuffling without significantly changing DAG frameworks, we propose S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework.
The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
SCache replaces the disk operations of shuffle write by the memory copy in map tasks and pre-fetches the shuffle data.
% Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
% In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
% Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle write and read from both map and reduce tasks.
Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
Second, SCache pre-schedules the reduce tasks without launching them and pre-fetches the shuffle data. 
Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
and avoid the extra early allocation of slots.

>>>>

One of the major \edited{deficiencies} of the shuffle phase is lacking coordinated management among different system resources \cite{fu2018efficient}.

@@

{\color{black}
To optimize the data shuffling without significantly changing DAG frameworks, we propose \emph{S(huffle)Cache}, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework.
The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
SCache replaces the disk operations of shuffle write by the memory copy in map tasks and pre-fetches the shuffle data.
% Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
% In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
% Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle write and read from both map and reduce tasks.
Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
Second, SCache pre-schedules the reduce tasks without launching them and pre-fetches the shuffle data. 
Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
and avoid the extra early allocation of slots.

### 2020-04-06 scache/jpdc/tex/motivation.tex
update

In this section, we first study the typical shuffle characteristics (\ref{shuffle pattern}), and then spot the opportunities to achieve shuffle optimization (\ref{observation}).
\subsection{Characteristic of Shuffle} \label{shuffle pattern}

@@

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
Can we mitigate or even remove the overhead of shuffle? 
To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
Unfortunately this defect exists not only in Spark \cite{apachespark} but also Hadoop MapReduce and Apache Tez \cite{tez}. 
A finer granularity resource allocation scheme should be provided to reduce these delays.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/util}
		\caption{Original Spark}
		\label{fig:util}
	\end{subfigure}
	\begin{subfigure}[b]{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/scache_util}
		\caption{Spark With SCache}
		\label{fig:scache_util}
	\end{subfigure}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
\end{figure*}

@@

\subsubsection{Multi-round Tasks Execution}\label{multi}
Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
% For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism. 
% Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
Since the shuffle data becomes available as soon as the end of a task's execution, 
and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

% Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data. 
To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.

>>>>

% In this section, we first study the typical shuffle characteristics (\ref{shuffle pattern}), and then spot the opportunities to achieve shuffle optimization (\ref{observation}).
% \subsection{Characteristic of Shuffle} \label{shuffle pattern}

@@

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
% Can we mitigate or even remove the overhead of shuffle? 
% To find the answers, 
We ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
Unfortunately this defect exists not only in Spark \cite{apachespark} but also Hadoop MapReduce and Apache Tez \cite{tez}. 
A finer granularity resource allocation scheme should be provided to reduce these delays.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
% \begin{figure*}
% 	\centering
% 	\begin{subfigure}[b]{0.47\linewidth}
% 		\includegraphics[width=\linewidth]{fig/util}
% 		\caption{Original Spark}
% 		\label{fig:util}
% 	\end{subfigure}
% 	\begin{subfigure}[b]{0.47\linewidth}
% 		\includegraphics[width=\linewidth]{fig/scache_util}
% 		\caption{Spark With SCache}
% 		\label{fig:scache_util}
% 	\end{subfigure}
% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
% \end{figure*}

@@

% \subsubsection{Multi-round Tasks Execution}\label{multi}
% Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
% For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
% For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism. 
% Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
% Since the shuffle data becomes available as soon as the end of a task's execution, 
% and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
% the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

% Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data. 
To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	% \item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.
